Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-13 manuscript/manuscript.tex
Changed textwidth for linewidth in manuscript
Added references to D-delta-grid-search figure in manuscript

\begin{figure*}
\centering
\includegraphics[width=\textwidth]
    {figures/density-based-discretization-algorithm.pdf}
\caption{
    Example intended to show how the density-based algorithm works.}
\label{fig:density-discretization-algorithm}
\end{figure*}

@@

Because the algorithm is intended to work with default $D$ and $\delta$ 
values that ensures these two conditions for every density function, 
the default value for $D$ cannot be lower than the one determined for 
the linear function.
That's why we can only choose the ($D$, $\delta$) points on which
$D \geq D_\text{linear}$.
In this way we can divide the $D$, $\delta$ space in two subregions: 
one with $D < D_\text{linear}$ and other with $D \ge D_\text{linear}$.
We can ignore points belonging to the former one and focus on the 
latter.

@@

With this definition in mind we can subdivide the subregion in two: one 
with points with $\delta > \delta_p$ and other with points with $\delta 
\le \delta_p$.

@@

Every point in the subregion with $\delta \le \delta_p$ will have a 
numerical error lower than the 0.1\% threshold, but they will always 
produce more discretizations than the ($D_\text{linear}$, $\delta_p$) 
point leading to non-efficient computations.

On the other hand, we have no a priori information about the numerical 
error of points with $\delta > \delta_p$.
Although, if we find a point with acceptable numerical error in this 
region, we know it will produce more discretizations than the 
($D_\text{linear}$, $\delta_p$) point.
This is due to the fact that even an increase in $\delta$ will produce 
less density-based discretizations, the increase in $D$ will introduce 
even more subdivisions not only in the radial direction, but 
also in the latitude and logitude ones.

>>>>

\begin{figure*}
\centering
\includegraphics[width=\linewidth]
    {figures/density-based-discretization-algorithm.pdf}
\caption{
    Example intended to show how the density-based algorithm works.}
\label{fig:density-discretization-algorithm}
\end{figure*}

@@

Because the algorithm is intended to work with default $D$ and $\delta$ 
values that ensures these two conditions for every density function, 
the default value for $D$ cannot be lower than the one determined for 
the linear function.
That's why we can only choose the ($D$, $\delta$) points on which
$D \geq D_\text{linear}$.
In this way we can divide the $D$, $\delta$ space in two subregions: 
one with $D < D_\text{linear}$ and other with $D \ge D_\text{linear}$.
We can ignore points belonging to the former one (region A on Figure 
\ref{fig:D-delta-grid-search}) and focus on the latter (regions B and C 
on Figure \ref{fig:D-delta-grid-search}).

@@

With this definition in mind we can subdivide the subregion in two: one 
with points with $\delta \le \delta_p$ (region B on Figure 
\ref{fig:D-delta-grid-search}) and other with points with $\delta > 
\delta_p$ (region C on Figure \ref{fig:D-delta-grid-search}).

@@

Every point in the subregion with $\delta \le \delta_p$ (region B on 
Figure \ref{fig:D-delta-grid-search}) will have a numerical error lower 
than the 0.1\% threshold, but they will always produce more 
discretizations than the ($D_\text{linear}$, $\delta_p$) point leading 
to non-efficient computations.

On the other hand, we have no a priori information about the numerical 
error of points with $\delta > \delta_p$ (region C on 
Figure \ref{fig:D-delta-grid-search}).
Although, if we find a point with acceptable numerical error in this 
region, we know it will produce more discretizations than the 
($D_\text{linear}$, $\delta_p$) point, leading to a non-efficient 
computation.
This is due to the fact that even an increase in $\delta$ will produce 
less density-based discretizations, the increase in $D$ will introduce 
even more subdivisions not only in the radial direction, but 
also in the latitude and longitude ones.

In conclusion, the ($D$, $\delta$) point that minimises the number of 
discretizations while keeping an acceptable numerical error under the 
0.1\% threshold is the one on which the ratio $D$ is equal to 
$D_\text{linear}$ and the delta ratio is $\delta_p$.
